### 2021-03-12 README.Rmd
update readme

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  comment = "#>"
)
taxadb:::td_disconnect()
```

@@

```{r}
birds <- bbs %>% 
  select(species) %>% 
  mutate(id = taxalight::get_ids(species, "col"))

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = TRUE,
  comment = "#>"
)
taxadb:::td_disconnect()
```

@@

```{r}
birds <- bbs %>% 
  select(species) %>% 
  mutate(id = get_ids(species, "col"))
